{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-31 brains-protocol.tex
Remove now obsolete note
Minor editorial changes

\rk{Add number of words to cells in heatmap}

@@

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1, independently of the feature considered.
In other words, beyond individual variation patterns, the substitution process is contractile for all the features, and each of them therefore exhibit a unique attractor.
Second, the comparison with $\mathcal{H}_0$ shows that there are two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.
The first class (Number of phonemes and Number of synonyms) are features for which the substitution process only brings words slightly closer to $\nu_{\phi}^0$, and no uniform bias can be observed
\TB{(furthermore, for these two features $\mathcal{H}_{00}$ stays inside the confidence intervals of the alteration, confirming that they are irrelevant for the substitution process)}.
\rk{Ajouter ce texte en bleu si tu décides de mettre les figures avec $\mathcal{H}_{00}$.}
The second class on the other hand (comprising Word frequency, Age of acquisition, and Clustering coefficient) are features for which the substitution process has a clear bias in one direction or the other.

Word frequency, with destination words always significantly above $\nu_{\phi}^0$, exhibits a strong bias towards more frequent words \TB{(this in turn confirms that substitution is more of a recall process than a familiarity process, since common words are favored over awkward ones)}.
\rk{Mais est-ce que c'est pas une inférence inverse que de dire ceci? i.e. on sait que "familiarity" implique un biais en faveur des mots awkards, et que "recall" implique un biais en faveur des mots fréquents, mais on peut pas vraiment tirer de conclusions en utilisant la réciproque, si?}.
The detailed variations of the Word frequency curve, despite an inflexion for high-frequency words, do not seem to follow any significant pattern.

Age of acquisition and Clustering coefficient, on the other hand, exhibit a clear negative bias for the substitution process. Both curves are significantly below their respective $\nu_{\phi}^0$ values, which is consistent with the literature on recall: words learned earlier and words with lower clustering coefficient are easier to produce than average~\citep{nelson2013activation,Zevin02}.
Clustering coefficient has the additional particularity that, on average, the destination word does not depend on the start word: a substitution will always produce words with a clustering coefficient near $\exp(-2.4) \simeq 0.1$.

>>>>

@@

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.
We can do a first striking observation: all graphs show the existence of a unique intersection of $\nu_{\phi}$ with $y=x$, while the slope of $\nu_{\phi}$ is smaller than 1, independently of the feature considered.
In other words, beyond individual variation patterns, the substitution process is contractile for all the features, and each of them therefore exhibits a unique attractor.
Second, the comparison with $\mathcal{H}_0$ shows that there are two classes of attractors, depending on whether (i) there is a triple intersection (of $y=x$, $\nu_{\phi}^0$ and $\nu_{\phi}$) or (ii) $\nu_{\phi}$ remains always above or below $\nu_{\phi}^0$.
The first class (Number of phonemes and Number of synonyms) are features for which the substitution process only brings words slightly closer to $\nu_{\phi}^0$, and no uniform bias can be observed
\TB{(furthermore, $\mathcal{H}_{00}$ stays inside the confidence intervals of $\nu_{\phi}$, confirming that these two features are irrelevant for the substitution process)}.
\rk{Ajouter ce texte en bleu si tu décides de mettre les figures avec $\mathcal{H}_{00}$.}
On the other hand, the second class (comprising Word frequency, Age of acquisition, and Clustering coefficient) are features for which the substitution process has a clear positive or negative bias.

Word frequency, with $\nu_{\phi}$ always significantly above $\nu_{\phi}^0$, exhibits a strong bias towards more frequent words \TB{(this in turn confirms that substitution is more of a recall process than a familiarity process, since common words are favored over awkward ones)}.
\rk{Mais est-ce que c'est pas une inférence inverse que de dire ceci? i.e. on sait qu'une tâche "familiarity/recognition" implique un biais en faveur des mots awkards, et qu'une tâche "recall" implique un biais en faveur des mots fréquents, mais on peut pas vraiment tirer de conclusions en utilisant la réciproque, si?}.
The detailed variations of the Word frequency curve, despite an inflexion for high-frequency words, do not seem to follow any significant pattern.

Age of acquisition and Clustering coefficient, on the other hand, exhibit a clear negative bias for the substitution process. Both curves are significantly below their respective $\nu_{\phi}^0$ values, which is consistent with the literature on recall: words learned earlier and words with lower clustering coefficient are easier to produce than average~\citep{nelson2013activation,Zevin02}.
Clustering coefficient has the additional particularity that, on average, the destination word does not depend on the start word; i.e. on average, substitutions will always produce words with a clustering coefficient around $\exp(-2.4) \simeq 0.1$.
